Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Resized Gas Corner images and added to tex file

The full-scale and bench-scale experiments were conducted over a period of several years whenever funding and laboratory availability coincided.  These experiments were conducted with the support of several engineering technicians from the NIST Fire Research Division, especially Roy McLane, Jay McElroy, Laurean DeLauter, and Anthony Chakalis.  Their assistance was essential. Their patience and attention to detail during this study is greatly appreciated

@@

\subsubsection{Gasoline}
\subsubsection{Polyurethane Foam}

>>>>

The full-scale and bench-scale experiments were conducted over a period of several years whenever funding and laboratory availability coincided.  These experiments were conducted with the support of several engineering technicians from the NIST Fire Research Division, especially Roy McLane, Jay McElroy, Laurean DeLauter, and Anthony Chakalis.  Their assistance was essential. Their patience and attention to detail during this study is greatly appreciated.

@@

Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fuleed burner in the corner position with walls of open back construction.

\begin{figure}[p]
	\includegraphics[width=1.3in]{../Figures/GBGas1C_P5270387}
	\includegraphics[width=1.3in]{../Figures/GBGas2C_P5270454}
	\includegraphics[width=1.3in]{../Figures/GBGas5C_P5270493}
	\includegraphics[width=1.3in]{../Figures/GBGas6C_P5270526} \\

	\includegraphics[width=1.3in]{../Figures/GBGas7C_P5270587}
	\includegraphics[width=1.3in]{../Figures/GBGas8C_P5270629}
	\includegraphics[width=1.3in]{../Figures/GBGas9C_P5270689}
	\includegraphics[width=1.3in]{../Figures/GBGas10C_IMG_9818} \\

	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner.}
	\label{Gas_Corner}
\end{figure}
